Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
use siunitx to pretty print numbers in the evaluation
also change figure environment -> table environment for the evaluation table

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{color}
\usepackage{graphics}
\usepackage{fancyvrb}
\usepackage{subfigure}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{minted}
\usepackage{breqn}

@@

\subsection{Software Corpus}
\begin{figure}
\begin{tabular}{|l|l|l|l|}
\hline
Package       & Files & Lines of code & Files analysed \\
\hline
UM            & \umFiles & \umLoC & \umparseOk  \\
E3MG          & \ethreemgeaFiles   & \ethreemgeaLoC & \ethreemgeaparseOk  \\
BLAS          & \blasFiles   & \blasLoC & \blasparseOk        \\
Hybrid4       & \hybridfourFiles    & \hybridfourLoC & \hybridfourparseOk         \\
GEOS-Chem     & \geoschemFiles   & \geoschemLoC & \geoschemparseOk       \\
Navier        & \navierFiles     & \navierLoC & \navierparseOk           \\
CP            & \computationalphysicstwoFiles    & \computationalphysicstwoLoC & \computationalphysicstwoparseOk           \\
\hline
\textbf{Total}& \overallFiles  & \overallLoC   & \overallparseOk  \\
\hline
\end{tabular}
\caption{Summary of software packages used for evaluation\label{fig:corpus}}
\end{figure}

Figure \ref{fig:corpus} shows summary statistics of the software packages used in our evaluation, all of which are written in Fortran 90 or Fortran 77. In total we analysed 1.1 million lines of code from 7 packages. The ``Files analysed'' column shows the number of files in each corpus that we were able to analyse with Camfort. The most common reasons for Camfort rejecting a file were either use of a C-preprocessor, or illegal use of language features from a more modern Fortran variant.

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{stmaryrd}
\usepackage{color}
\usepackage{graphics}
\usepackage{fancyvrb}
\usepackage{subfigure}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{minted}
\usepackage{breqn}
\usepackage{siunitx} % For pretty-printing numeric values and SI units
                     % of measure. e.g., the tabular column type S is
                     % used to print nice-looking tables of numbers.
\sisetup{group-separator={,},group-minimum-digits={3},output-decimal-marker={.}}

@@

\subsection{Software Corpus}
\begin{table}
\centering
\sisetup{
  table-format = 7,
  table-number-alignment = right
}
\begin{tabular}{|l|S|S|S|}
\hline
Package       & {Files} & {Lines of code} & {Files analysed} \\ % braces prevent headers from being formatted as numbers
\hline
UM            & \umFiles & \umLoC & \umparseOk  \\
E3MG          & \ethreemgeaFiles   & \ethreemgeaLoC & \ethreemgeaparseOk  \\
BLAS          & \blasFiles   & \blasLoC & \blasparseOk        \\
Hybrid4       & \hybridfourFiles    & \hybridfourLoC & \hybridfourparseOk         \\
GEOS-Chem     & \geoschemFiles   & \geoschemLoC & \geoschemparseOk       \\
Navier        & \navierFiles     & \navierLoC & \navierparseOk           \\
CP            & \computationalphysicstwoFiles    & \computationalphysicstwoLoC & \computationalphysicstwoparseOk           \\
\hline
\textbf{Total}& \overallFiles  & \overallLoC   & \overallparseOk  \\
\hline
\end{tabular}
\caption{Summary of software packages used for evaluation\label{tab:corpus}}
\end{table}

Table~\ref{tab:corpus} shows summary statistics of the software
packages used in our evaluation, all of which are written in Fortran
90 or Fortran 77. In total we analysed 1.1 million lines of code from
7 packages. The ``Files analysed'' column shows the number of files in
each corpus that we were able to analyse with Camfort. The most common
reasons for Camfort rejecting a file were either use of a
C-preprocessor, or illegal use of language features from a more modern
Fortran variant.
